---
title: "KOGPSY"
description: |
  Welcome to the website for *Kognitionspsychologie II* FS24 ([23263-02](https://vorlesungsverzeichnis.unibas.ch/de/home?id=280442))
  
  Instructors: [Loreen Tisdall](https://loreentisdall.github.io) and [Rui Mata](https://psychologie.unibas.ch/de/personen/rui-mata/about-me/), University of Basel
  
  **WEBSITE UNDER CONSTRUCTION:** Last updated `r format(Sys.time(), "%a %b %d %X %Y")`
  
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

![Thinking, feeling, willing are simply words we use to describe different ways of using one's brain! <span>Photo by <a href="https://unsplash.com/@jessemartini?utm_source=unsplash&amp;utm_medium=referral&amp;utm_content=creditCopyText">Jesse Martini</a> on <a href="https://unsplash.com/s/photos/brain?utm_source=unsplash&amp;utm_medium=referral&amp;utm_content=creditCopyText">Unsplash</a></span>](photos/jesse-martini-Iod3vdjKE1E-unsplash.jpg)

# Session information

Sessions take place Tuesdays, 10.15-11.45, Biozentrum, Maurice E. Müller Saal U1.111. 

::: l-body
| # | Date     | Topic                         | Slides |
|---| ---------|-------------------------------|--------|
| 1 | 27.02.2024 | [Session 1: Introduction](session1.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session1.pdf)|
| 2 | 05.03.2024 | [Session 2: Intelligence](session2.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session2.pdf)|
| 3 | 12.03.2024 | [Session 3: Spatial cognition](session3.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session3.pdf)|
| 4 | 19.03.2024 | [Session 4: Numerical cognition](session4.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session4.pdf)|
| 5 | 26.03.2024 | [Session 5: Emotion](session5.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session5.pdf)|
| 6 | 09.04.2024 | [Session 6: Social cognition](session6.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session6.pdf)|
| 7 | 16.04.2024 | [Session 7: Motivation](session7.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session7.pdf)|
| 8 | 23.04.2024 | [Session 8: Language](session8.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session8.pdf)|
| 9 | 30.04.2024 | [Session 9: Knowing](session9.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session9.pdf)|
|10 | 07.05.2024 | [Session 10: Consciousness](session10.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session10.pdf)|
|11 | 14.05.2024 | [Session 11: What's next](session11.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session11.pdf)|
|12 | 21.05.2024 | [Session 12: Q&A](session12.html) | [pdf](https://github.com/matarui/kogpsy/raw/main/docs/presentations/KPII_session12.pdf)|
|13 | 04.06.2024 | [Exam](exam.html) | |
:::

```{r, include=FALSE}
# https://github.com/matarui/kogpsy/raw/main/docs/presentations/KOGPSY_session1.pdf
```

# What is this course about?

This course aims to give a broad introduction to central topics in psychology, with a focus on mechanistic explanations of cognition, emotion, and motivation. 

# What can you expect to learn?

By completing the course you can expect to...

- learn about central theories and models in key areas of psychology
- become familiarized with common methods used in psychology
- learn about examples of applications of psychology to real-world contexts
- reflect about the need for pluralistic explanations in psychology

# How should you use this website?

This website is designed to help course participants get an overview of the course and the course materials (e.g., slides, recommended readings). Recommended readings cover central topics discussed in each session and, therefore, they represent a central resource for a thorough preparation for the exam. A [FAQ](https://adam.unibas.ch/goto_adam_crs_1687450.html) forum is available on ADAM. 